Lexicalized Domain Representations for Neural Machine Translation

### 2019-08-28 2019/iwslt/submission.tex
light

\section{Conclusions}
In this paper, we have presented a new technique for multi-domain machine translation,  adapting the ``frustratingly easy'' idea of \cite{Daume07frustratingly} to two standard NMT architectures. 
Our experiments have shown that for both architectures and for two language pairs, our multi-domain models improve over several baselines of the literature and that it is robust to noise in domain labels. It is noticeable that these results are obtained without impacting the architecture or training complexity
, making our approach a simple baseline for further studies in multi-domain translation
.
We have also shown that our approach can dynamically handle new domains; and that the domain-specific embeddings often reflect differences of senses. In our future work, we intend to develop these ideas so as to make the architecture more self-configurable and able to adapt the size of the domain-specific regions depending upon the actual variation of use across domains; we also would like to find additional ways to make the architecture able to integrate an arbitrary number of new domains in a dynamic fashion, as this is an important requirement in industrial systems.

>>>>

\section{Conclusions}
In this paper, we have presented a new technique for multi-domain machine translation,  adapting the ``frustratingly easy'' idea of \cite{Daume07frustratingly} to two standard NMT architectures. 
Our experiments have shown that for both architectures and for two language pairs, our multi-domain models improve over several baselines of the literature and that it is robust to noise in domain labels. 
It is noticeable that these results are obtained without impacting the architecture or training complexity
, making our approach a simple baseline for further studies in multi-domain translation.
We have also shown that our approach can dynamically handle new domains; and that the domain-specific embeddings often reflect differences of senses. In our future work, we intend to develop these ideas so as to make the architecture more self-configurable and able to adapt the size of the domain-specific regions depending upon the actual variation of use across domains; we also would like to find additional ways to make the architecture able to integrate an arbitrary number of new domains in a dynamic fashion, as this is an important requirement in industrial systems.
